Inferring stellar rotation periods using Gaussian processes

### 2017-01-25 documents/ms.tex
fixed latex typo with underscore
transits masked

In order to test this rotation period inference method on real data,
we applied it to a set of \nkois\ \Kepler\ Object of Interest (KOI)
host stars, \nkoimcq\ of which had rotation periods previously measured by 
the ACF method by \citet{Mcquillan2013}.  We use the pipeline-corrected flux 
(\texttt{pdcsap_flux} column in the \Kepler\ light curve table), median-normalized
and unit-subtracted.  As with the simulated light curves, we randomly subsample each 
light curve by a factor of 30 and split it into segments of about 300 points
for the purposes of evaluating the likelihood.  We also follow the same MCMC
fitting procedure as with the simulated data, using the ACF-based prior as before.

>>>>

In order to test this rotation period inference method on real data,
we applied it to a set of \nkois\ \Kepler\ Object of Interest (KOI)
host stars, \nkoimcq\ of which had rotation periods previously measured by 
the ACF method by \citet{Mcquillan2013}.  We use the pipeline-corrected flux 
(\texttt{pdcsap\_flux} column in the \Kepler\ light curve table), median-normalized
and unit-subtracted, and mask out all known transiting planet candidate signals.  
As with the simulated light curves, we randomly subsample each 
light curve by a factor of 30 and split it into segments of about 300 points
for the purposes of evaluating the likelihood.  We also follow the same MCMC
fitting procedure as with the simulated data, using the ACF-based prior as before.
